\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Timur Zheltenkov} \\
  \small +4915234640640 $|$ \href{mailto:alex@email.com}{zheltenkovtimur@email.com} $|$ 
  \href{https://linkedin.com/in/burhan-webb}{linkedin.com/in/timurzheltenkov} $|$
  \href{https://github.com/zwayth}{github.com/timurenk0}
\end{center}

\section*{Summary}
Software Engineer student at GISMA University Of Applied Sciences. Dynamic professional with 3+ years of experience in web development. Proficient in Python, HTML, CSS, ReactJS, JavaScript, and SQL. Skilled in creating seamless, efficient applications with robust back-end functionalities and dynamic, user-friendly interfaces. Proven track record in delivering high-quality solutions.

\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Programming Languages}: Python, JavaScript, SQL, ReactJS}
  \resumeItem{\textbf{Libraries \& Tools}: NumPy, OpenCV, Git, Docker}
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList
  \resumeSubheading
      {Responsive Landing Page Example}{Jan 2023 -- Mar 2023}
      {Front-end web development}{HTML, CSS}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Built a landing page for the furniture-selling website.}
          \resumeItem{\textbullet\ Utilized TailWind framework.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Platform For Teachers Application}{Jun 2023 -- Present} 
      {Front- and Back-end web development}{HTML, CSS, JavaScript, Firebase}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Built an easy-to-use application for the private school.}
          \resumeItem{\textbullet\ Implemented Firebase Google database system}
          \resumeItem{\textbullet\ Deployed the application on the server for better user experience}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingList
  \resumeSubheading
      {HACKATHON}{Jun 2023 -- Jun 2023}
      {Building application for the start-up company}{Berlin, Germany}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Built working model and deployed the web application for the company}
          \resumeItem{\textbullet\ Optimized model performance and ensured data quality}
          \resumeItem{\textbullet\ Collaborated with cross-functional teams to deliver AI solutions}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {STEP IT Academy}{Baku, Azerbaijan}
      {Python programming, 3d modeling, working with photo, video and audio editors}{Sep 2018 -- Oct 2023}
  \resumeSubheading
      {GISMA University Of Applied Sciences, Potsdam}{Potsdam, Germany}
      {B.S. in Software Engineering}{Oct 2023 -- Present}
\resumeSubHeadingListEnd

\end{document}